% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\definecolor{mygrey}{gray}{0.85}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue
}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

\begin{document}

    \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
    \textbf{\large William H. Martins} & +55 51 9626 1149 \\
    Avenida Bento Gonçalves, 1515      & \href{mailto:wwwhmartins@gmail.com}{wwwhmartins@gmail.com} \\
    Porto Alegre - Rio Grande do Sul   & \href{https://github.com/wmartins}{github.com/wmartins} \\
    Brazil                             & \href{https://linkedin.com/in/wwwhmartins}{linkedin.com/in/wwwhmartins}
    \end{tabular*}
    \\
    \vspace{0.1in}

    \resheading{Education}
    \begin{itemize}
        \item
            \ressubheading
                {Pontifical Catholic University of Rio Grande do Sul}
                {Porto Alegre - Rio Grande do Sul - Brazil}
                {Bachelor of Science in Computer Science}
                {Feb. 2012 - Dec. 2016}

        \item
            \ressubheading
                {Federal Institute of Rio Grande do Sul}
                {Charqueadas - Rio Grande do Sul - Brazil}
                {Information Systems Technician}
                {Feb. 2008 - Dec. 2011}
    \end{itemize}

    \resheading{Work Experience}
    \begin{itemize}
        \item
            \ressubheading
                {ADP - Automatic Data Processing}
                {Porto Alegre - Rio Grande do Sul - Brazil}
                {Software Developer}
                {March 2015 - Present}
            \begin{itemize}
                \resitem{Part of development team, being responsible for both front-end and back-end code.}
                \resitem{Helped team to establish an effective git flow that allowed us to develop new features and ship code with confidence.}
                \resitem{Responsible for refactoring tests to a back-end application that allowed us to code new features with confidence.}
                \resitem{Created a tiny and effective CSS framework used to prototype and code new pages.}
            \end{itemize}

        \item
            \ressubheading
                {dEx digital}
                {Porto Alegre - Rio Grande do Sul - Brazil}
                {Front-End Developer}
                {October 2013 - February 2015}
            \begin{itemize}
                \resitem{Responsible for coding responsive websites to company clients.}
                \resitem{Created a new front-end workflow, using new tools and technologies.}
                \resitem{Helped back-end team to code some features.}
            \end{itemize}

        \item
            \ressubheading
                {Ockan Networks}
                {Porto Alegre - Rio Grande do Sul - Brazil}
                {Front-End Developer}
                {January 2012 - October 2013}
            \begin{itemize}
                \resitem{Part of development/analysis team, being responsible to collect system requirements and build web solutions to them.}
                \resitem{Introduced a new framework that made team a lot more productive.}
            \end{itemize}

        \item
            \ressubheading
                {TMW Telecom}
                {Arroio dos Ratos - Rio Grande do Sul - Brazil}
                {Web Developer}
                {January 2011 - December 2011}
            \begin{itemize}
                \resitem{Part of development/analysis team, being responsible to collect system requirements and build web solutions to them.}
                \resitem{Created a new application to manage company workflow.}
            \end{itemize}
    \end{itemize}

    \resheading{Skills}
    \begin{description}
        \item[Languages]
            HTML, CSS, JavaScript, NodeJS, C/C++, Python, Java, PHP, \LaTeX.
        \item[Databases]
            PostgreSQL, MySQL, MongoDB, Oracle.
        \item[Web Technologies]
            PostCSS, webpack, SASS, LESS, ReactJS.
        \item[Miscellaneous]
            Linux, Git, Bash, Docker, GitHub.
    \end{description}

    \resheading{Open Source Projects}
    \begin{itemize}
        \item
            \ressubheading
                {Mongration}
                {\href{https://github.com/awapps/mongration}{github.com/awapps/mongration}}
                {MongoDB migration framework}
                {}
    \end{itemize}

\end{document}
